Rebuttal JMLR 14-133

### 2014-09-05 pkg/partykit/inst/mloss/review2/p2p.tex
added some comments
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@594 255f4249-2263-4417-b1ea-8498779e27a7

@@

@@

\textit{Quibbles and queries are:}
\begin{enumerate}
\item 
\textit{
The legend for Table 1 begins: ``Selected tree algorithms than can be
interfaced through partykit...''  Surely it is the output from selected
implementations that can be interfaced, not the algorithm used.  The word
‘algorithm’ seems to me anyway inappropriate in this context.  The same (or
very similar) algorithm may have different implementations.  Different
methods with their inevitably different algorithms (including, in partykit:
classical `constant’ trees, model-based trees, and conditional inference
trees) further wide widen the range of implementations.}

@@

\item 
\textit{
The distinction between implementation (what the authors call `algorithm’)
and output is crucial also because as far as I am able to judge, partykit’s
abilities are limited to taking over and processing some part only of the
output from, e.g., R’s rpart package.  As I understand, there is no ability
to use or process, e.g., results from rpart’s on the fly cross-validation. 
Would it be straightforward to incorporate structure that is able to
accommodate such information?  See also point 3 that now follows.}

@@

@@

\textit{
The paper describes an R library,}

an R package, actually.

\textit{ `partykit', that appears to be a unified
way of representing decision tree structures (or recursive partitioning
structures) in R and manipulating or visualizing them.  The authors note
that their library contains support for representing the output of trees
created with other packages, and the paper appears to function as a very
basic tutorial with links to very detailed R vignettes.  The package also
implements a few of the authors' own recursive partitioning algorithms.}

@@

und?

@@

added

@@

>>>>

mention: previous round of reviews asked for this format of the paper

@@

yes

maybe worth mentioning: due to the flexible infrastructure, the two
specialized methods (ctree, mob) have become more flexible compared to
earlier implementations (especially the mob framework)

@@

\textit{Quibbles and queries are:}
\begin{enumerate}
\item 
\textit{
The legend for Table 1 begins: ``Selected tree algorithms than can be
interfaced through partykit...''  Surely it is the output from selected
implementations that can be interfaced, not the algorithm used.  The word
`algorithm' seems to me anyway inappropriate in this context.  The same (or
very similar) algorithm may have different implementations.  Different
methods with their inevitably different algorithms (including, in partykit:
classical `constant' trees, model-based trees, and conditional inference
trees) further wide widen the range of implementations.}

@@

\item 
\textit{
The distinction between implementation (what the authors call `algorithm')
and output is crucial also because as far as I am able to judge, partykit's
abilities are limited to taking over and processing some part only of the
output from, e.g., R's rpart package.  As I understand, there is no ability
to use or process, e.g., results from rpart's on the fly cross-validation. 
Would it be straightforward to incorporate structure that is able to
accommodate such information?  See also point 3 that now follows.}

@@

But probably also rephrase...

@@

\textit{
The paper describes an R library, `partykit', that appears to be a unified
way of representing decision tree structures (or recursive partitioning
structures) in R and manipulating or visualizing them.  The authors note
that their library contains support for representing the output of trees
created with other packages, and the paper appears to function as a very
basic tutorial with links to very detailed R vignettes.  The package also
implements a few of the authors' own recursive partitioning algorithms.}

mention: previous round of reviews asked for this format

@@

not a big software project, just two main developers, hence sometimes longer breaks

we feel that this is not an indicator of the quality of the code, though

@@

E-mails to the maintainer address were always possible and used fairly regularly
by both end-users and other package developers. A mailing list was added now.

@@

examples: CTree and display of p-values, J4.8 and multiway splits
